Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-02 abstract.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

We study the quantum quench problem for a class of bosonic conformal interfaces by computing the Loschmidt echo and the bipartite fidelity. The quench can be viewed as a sudden change of boundary conditions parameterized by $\theta$ when connecting two one-dimensional critical systems. They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface. The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$. We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

>>>>

We study the quantum quench problem for a class of bosonic conformal interfaces by computing the Loschmidt echo and the bipartite fidelity. The quench can be viewed as a sudden change of boundary conditions parameterized by $\theta$ when connecting two one-dimensional critical systems. They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface. The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartite fidelity as $L^{-\frac{\alpha}{2}}$. We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. Possible physical realizations of these interfaces include for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

### 2017-10-02 analy_eval.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

The Loschmidt echo can be evaluated in the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, the diagram becomes the cylinder partition function between the two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to come from the Schwartzian and outer circle regulator.

>>>>

The Loschmidt echo can be evaluated in the same way. Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, the diagram becomes the cylinder partition function between the two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformations. In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to come from the Schwartzian and outer circle regulator.

### 2017-10-02 def_fidel_echo.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams. We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries).

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams. We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries). {\color{red}We would like to emphasize that all the path-integral spacetime diagrams are in the Euclidean space, and the analytic continuation will be performed only for the final results.}

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity {\color{red}($L$ is the finite size of the system)} and $\ln \tau$ in Loschmidt echo {\color{red}($\tau$ is the imaginary time)}. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}
where $\tau$ is the imaginary time.

The tip of the slit is no longer a {\color{red}corner singularity\cite{cardy_finite-size_1988}} with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-10-02 general_formulation.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states. For example, one may use the current operator rather than the Virasoro generator to solve the zero momentum flow condition. This idea dates back to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state. The interface obtained is actually the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.

Assume two free boson fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. The interface located at $x = 0$ is characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum components of the stress tensor are continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix},\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix},
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

@@

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, 
{\color{red}whose transmission coefficient
%and reflection coefficients 
can be read off from the scattering matrices
\begin{eqnarray}\begin{aligned}
t = \sin2\theta.
\end{aligned}\end{eqnarray}
}
We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

>>>>

Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states. For example, one may use the current operator rather than the Virasoro generator to solve the zero-momentum flow condition. This idea dates to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state. The interface obtained is the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.

Assume two free boson fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. The interface located at $x = 0$ is characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum components of the stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix},\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix},
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

@@

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, 
{\color{red}whose transmission coefficient
%and reflection coefficients 
can be read off from the scattering matrices
\begin{eqnarray}\begin{aligned}
t = \sin2\theta.
\end{aligned}\end{eqnarray}
}
We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

### 2017-10-02 intro.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.

This paper includes several appendices for technical details. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Up until this point, we work exclusively with the oscillator modes of the free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.

>>>>

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally, we conclude in Sec.~\ref{sec:conclusion}.

This paper includes several appendices for technical details. In App.~\ref{app:lambda_12}, we present the detailed calculation of the free energy for the above-mentioned interfaces. In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text. Up to this point, we work exclusively with the oscillator modes of the free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore, the results remain valid in the physical situation of connecting two compactified bosons of different radii. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation are presented in App.~\ref{app:comp_fid_echo}.

### 2017-10-02 num_result.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

We start with the process in {\color{red}Eq.~\eqref{eq:DDDD}}, 
%\begin{equation}
%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
%\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

We also calculated the companion process
\begin{equation}
 \text{NN}+\text{NN}\rightarrow\lambda+\text{NN},
\end{equation}
and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}. We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$. While the short time decay pattern is different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity. We therefore do not present the result here.

Next we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.}The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

>>>>

{\color{red}We first consider the process in Eq.~\eqref{eq:DDDD} for a lattice with $3000$ sites}, 
%\begin{equation}
%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
%\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

We also calculated the companion process
\begin{equation}
 \text{NN}+\text{NN}\rightarrow\lambda+\text{NN},
\end{equation}
and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}. We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$. While the short time decay pattern is different from the DD case, the long-time behavior and exponents remain the same for both echo and fidelity. We therefore do not present the result here.

Next, we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. {\color{red}We worked with a system containing $35000$ sites.} A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.} The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}
